Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-14 ms.tex
added caption for low-frequency emission prediction comparison figure, auditing for nside formatting

With $p$ denoting a single nside=64 HEALPix pixel \citep{healpix} in the maps 
$\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
sources, and the constant offset of $\S$\ref{sec:zp_abs} removed, smoothed to 
$1^{\circ}$ resolution. $\mathcal{I}_{\nu_i}$ is the corresponding $1^{\circ}$ 
resolution \PLANCK~HFI map with zodiacal emission, CMB anisotropies, and
compact sources removed. In the context of Equation \ref{equ:dip}, $\nu_i \in$ 
\{100, 143, 217, 353, 545\} GHz. Note that $\mathcal{I}_{\nu_i}$ is always in
the native units of the relevant \PLANCK~band. $\mathcal{D}$ is a scaling of 
the Solar dipole pattern oriented toward 
$(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit amplitude. Because 
$\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we have an 
overconstrained linear model with three parameters: $m$, $d$, and $b$. $m$ 
represents the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz 
assuming they are linearly related. $d$ is the residual Solar dipole amplitude,
and its best-fit value represents the scaling of the Solar dipole that makes 
the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly linear. $b$ 
represents the constant offset that must be subtracted from the band $\nu_i$ 
map to make its zero level consistent with that of the 857 GHz map. For each 
band $\nu_i$, we obtain estimates of $m$, $d$, and $b$ by performing a linear 
least squares fit with uniform weights and iterative outlier rejection. Figure 
\ref{fig:dip} shows scatterplots of the band $\nu_i$ versus 857 GHz correlation
 before and after correcting for the best-fit offset and residual dipole, for 
each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only are the tightened 
correlations striking in these scatterplots, but the residual dipole 
subtractions appear very successful in the two-dimensional band $\nu_i$ maps 
themselves. Before performing thermal dust fits, we therefore subtract the 
best-fit $b$ and $d\mathcal{D}$ from each band $\nu_i$ map. The best-fit 
offsets and residual dipole amplitudes are listed in Table \ref{table:offs},
along with other important per-band parameters, such as the fractional 
multiplicative calibration uncertainty $c_{\nu}$.

@@

\begin{figure}
\begin{center}
\epsfig{file=sed.eps, width=3.3in}
\caption{\label{fig:sed} Planck SED for a single nside=2048 pixel in the 
Polaris region. Note that the two lowest-frequency data points (\PLANCK~100, 
143 GHz) were not used in our fit, while the three lowest-frequency data
points were not used in the \cite{planckdust} fit.}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\epsfig{file=posteriors.eps, width=7.0in}
\caption{Gridded posterior PDFs for three nside=2048 pixels. Red crosses mark 
the best-fit parameters based on our Markov chain sampling of the posterior. 
The posterior distributions are in general extremely well-behaved, showing
no multimodality or other pathological qualities. Our MCMC parameter 
estimates coincide well with the peaks in the gridded posteriors. The 
colorscale is linear in $log(P)$, with black representing the maximum of 
$log(P)$ and white representing $max(log(P))-5$. Left: Low S/N pixel at 
high-latitude in Galactic north. Center: High S/N pixel in the Polaris region. 
Right: Low S/N pixel at high-latitude in the Galactic south.}
\end{center}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\epsfig{file=compare_lofreq.eps, width=6.8in}
\caption{\label{fig:lofreq} Comparison of low-frequency thermal dust emission 
predictions.}
\end{center}
\end{figure*}

@@

>>>>

With $p$ denoting a single $N_{side}$=64 HEALPix pixel \citep{healpix} in the 
maps $\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
sources, and the constant offset of $\S$\ref{sec:zp_abs} removed, smoothed to 
$1^{\circ}$ resolution. $\mathcal{I}_{\nu_i}$ is the corresponding $1^{\circ}$ 
resolution \PLANCK~HFI map with zodiacal emission, CMB anisotropies, and
compact sources removed. In the context of Equation \ref{equ:dip}, $\nu_i \in$ 
\{100, 143, 217, 353, 545\} GHz. Note that $\mathcal{I}_{\nu_i}$ is always in
the native units of the relevant \PLANCK~band. $\mathcal{D}$ is a scaling of 
the Solar dipole pattern oriented toward 
$(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit amplitude. Because 
$\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we have an 
overconstrained linear model with three parameters: $m$, $d$, and $b$. $m$ 
represents the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz 
assuming they are linearly related. $d$ is the residual Solar dipole amplitude,
and its best-fit value represents the scaling of the Solar dipole that makes 
the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly linear. $b$ 
represents the constant offset that must be subtracted from the band $\nu_i$ 
map to make its zero level consistent with that of the 857 GHz map. For each 
band $\nu_i$, we obtain estimates of $m$, $d$, and $b$ by performing a linear 
least squares fit with uniform weights and iterative outlier rejection. Figure 
\ref{fig:dip} shows scatterplots of the band $\nu_i$ versus 857 GHz correlation
 before and after correcting for the best-fit offset and residual dipole, for 
each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only are the tightened 
correlations striking in these scatterplots, but the residual dipole 
subtractions appear very successful in the two-dimensional band $\nu_i$ maps 
themselves. Before performing thermal dust fits, we therefore subtract the 
best-fit $b$ and $d\mathcal{D}$ from each band $\nu_i$ map. The best-fit 
offsets and residual dipole amplitudes are listed in Table \ref{table:offs},
along with other important per-band parameters, such as the fractional 
multiplicative calibration uncertainty $c_{\nu}$.

@@

\begin{figure}
\begin{center}
\epsfig{file=sed.eps, width=3.3in}
\caption{\label{fig:sed} Planck SED for a single $N_{side}$=2048 pixel in the 
Polaris region. Note that the two lowest-frequency data points (\PLANCK~100, 
143 GHz) were not used in our fit, while the three lowest-frequency data
points were not used in the \cite{planckdust} fit.}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\epsfig{file=posteriors.eps, width=7.0in}
\caption{Gridded posterior PDFs for three $N_{side}$=2048 pixels. Red crosses 
mark the best-fit parameters based on our Markov chain sampling of the 
posterior. The posterior distributions are in general extremely well-behaved, 
showing no multimodality or other pathological qualities. Our MCMC parameter 
estimates coincide well with the peaks in the gridded posteriors. The 
colorscale is linear in $log(P)$, with black representing the maximum of 
$log(P)$ and white representing $max(log(P))-5$. Left: Low S/N pixel at 
high latitude in the Galactic north. Center: High S/N pixel in the Polaris 
region. Right: Low S/N pixel at high latitude in the Galactic south.}
\end{center}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\epsfig{file=compare_lofreq.eps, width=6.8in}
\caption{\label{fig:lofreq} Comparison between low-frequency thermal dust 
emission predictions from our best-fit two-component model (Table 
\ref{tab:global}, model 2) and those of \cite{planckdust}. The top row shows
scatterplots of the \cite{planckdust} predictions versus observed \PLANCK~100 
GHz (left), \PLANCK~143 GHz (center) and \PLANCK~217 GHz (right). The bottom 
row shows scatterplots of the corresponding two-component predictions versus
\PLANCK~observations. In all cases, the blue line indicates the best-fit linear
relationship, while the red line represents a perfect match between predictions
and observations. The lines of best-fit illustrate that the single-MBB model 
systematically underpredicts emission (in the multiplicative sense) by 18.8\%, 
12.6\% and 7.9\% at 100, 143 and 217 GHz respectively. On the other hand, by 
the same metric, the two-component model predictions at 100-217 GHz are always 
accurate to within $\le$2.2\%.}
\end{center}
\end{figure*}

@@

% could add a sentence noting that similar zodi corrections are evident
% in all existing, comparable temperature map data products : Planck 2013a,
% SFD98 and FDS99
